Test Data

### 2022-07-07 01_studies/01_Laborstudie ProVisioNET/Fitbit/fitbit_proj_final/Test Data.Rmd

---
title: "R Notebook"
output: html_notebook
---
# Packages

```{r}
library(needs)
needs(tidyverse,
      lubridate,
      janitor)
```

# Daten

```{r}
df_acc <- read_tsv(file = "data/ProVisioNET.tsv") %>% 
  clean_names()
```
```{r}
df_acc <- transmute(df_acc,
                    ID = str_replace(str_sub(participant_name,
                                             start = 19,
                                             end = 21
                                             ),
                                     pattern = "_",
                                     replacement = ""
                                     ),
                    gyro_x = as.numeric(str_replace(gyro_x,
                                                    pattern = ",",
                                                    replacement = "."
                                                    )
                                        ),
                    gyro_y = as.numeric(str_replace(gyro_y,
                                                    pattern = ",",
                                                    replacement = "."
                                                    )
                                        ),
                    acc_x = as.numeric(str_replace(accelerometer_x,
                                                    pattern = ",",
                                                    replacement = "."
                                                    )
                                        ),
                    acc_z = as.numeric(str_replace(accelerometer_z,
                                                    pattern = ",",
                                                    replacement = "."
                                                    )
                                        ),
                    time = as.numeric(milliseconds(recording_timestamp
                                                   )
                                      ),
                    sensor = sensor,
                    meter_x = rep(0),
                    meter_z = rep(0)
                    ) %>% 
  filter(as.numeric(ID) > 100) %>%
  select(!contains("gyro")) %>%
  na.omit() %>%
  select(!"sensor")

# df_acc <- df_acc %>% 
#   filter(as.numeric(ID) > 100)
# 
# df_acc_acc <- df_acc %>%
#   filter(sensor == "Accelerometer") %>%
#   select(!contains("gyro")) %>%
#   pivot_longer(cols = c(acc_x, acc_z),
#                names_to = "acc")
# 
# df_acc_gyro <- df_acc %>%
#   filter(sensor == "Gyroscope") %>%
#   select(!contains("acc"))
```

```{r}
plot_acc <- 
ggplot(data = df_acc_acc,
       mapping = aes(x = time,
                     y = value
                     )
       ) +
  geom_path() +
  geom_path() +
  facet_grid(rows = vars(ID),
             cols = vars(acc)
             )

ggsave(plot = plot_acc,
       filename = "Plots/plot_acc.pdf",
       height = 10,
       width = 5)

# df_sum <- 
# df_acc_acc %>% 
#   group_by(acc, ID) %>%
#   summarize(sum = sum(abs(value)),
#             time = max(time)
#             )
```

```{r}
# First step: create tibbles for each individual.
for (i in unique(df_acc$ID)) {

  df <- filter(df_acc,
               ID == i
               )

@@

for (i in unique(df_acc$ID)) {

@@

df_meter_all <- 
  mget(ls(pattern = "meter")) %>%
  bind_rows() %>% 
  group_by(ID) %>%
  summarise(meter_x = sum(abs(meter_x)),
            meter_z = sum(abs(meter_z)))

@@

$$\Delta x_{d,i} = 0.5 (t_{i-1}-t_{i})^2, \text{ with }i=2,...,t_n; d = z,x$$
$$x_d=\sum_{i=1}^n |\Delta x_{d,i}|, \text{ with }i=2,...,t_n; d = z,x$$
$$\sum x=\sqrt{x_z^2+x_x^2}$$

- 4 Szenarien (still, still + kopf, viel gehen, wenig gehen, fahrstuhl, treppe) + whatever

```{r}
saveRDS(object = df_meter_all,
        file = "data/df_meter_all.rds")

rm(list = ls())
```

# Plot

```{r}
ggplot(data = df_acc_hr,
       mapping = aes(x = mean,
                      y = ges
                      )
        ) +
   geom_point(mapping = aes(color = status)) +
   geom_smooth(method = "lm",
               se = F) +
   labs(x = "Average Heart Rate\n(in Beats per Minute)",
        y = "Meters Walked\n(in Meters)")
```

>>>>

---
title: "Test Data"
output: html_notebook
---

# Packages

```{r}
library(needs)
needs(tidyverse,
      janitor,
      lubridate)
```

# Data

```{r message=FALSE}
df_test <- read_tsv(file = "data/Acc_Test_Data.tsv") %>% 
  clean_names()
```

# Let the wrangle begin

```{r}
df_test <- 
  df_test %>%
  transmute(time = as.numeric(milliseconds(recording_timestamp_ms
                                           )
                              ),
            name = participant_name,
            acc_x = as.numeric(str_replace(accelerometer_x_m_s2,
                                           pattern = ",",
                                           replacement = "."
                                           )
                               ),
            acc_z = as.numeric(str_replace(accelerometer_z_m_s2,
                                           pattern = ",",
                                           replacement = "."
                                           )
                               )
            )
```

# Loops

```{r}
# First step: create tibbles for each individual.
for (i in unique(df_test$name)) {

  df <- filter(df_test,
               name == i
               )

@@

for (i in unique(df_test$name)) {

@@

df_meter_all <- 
  mget(ls(pattern = "meter")) %>%
  bind_rows() %>% 
  group_by(ID) %>%
  summarise(meter_x = sum(abs(meter_x)),
            meter_z = sum(abs(meter_z))
            )

@@

# Ergebnisse

```{r}
df_meter_all
```

```{r}
df_test %>%
  pivot_longer(cols = contains("acc"),
               names_to = "acc") %>%
ggplot(mapping = aes(x = time,
                     y = value
                     )
       ) +
  geom_path() +
  facet_grid(rows = vars(name),
             cols = vars(acc) 
             ) +
  theme(strip.text.y = element_text(angle = 0))
```
